%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Mock Interviewing Platform} $|$ \emph{Next.js, FastAPI, Python, Vosk, TextBlob, MediaPipe, SQLite, Terraform }}{July 2025}
          \resumeItemListStart
            \resumeItem{Built a AI-driven mock interview app using \textbf{Next.js} and \textbf{FastAPI}, using speech transcription, sentiment analysis, and eye-tracking.}
            \resumeItem{Automated infrastructure setup using \textbf{Terraform}, accelerating deployment and simplifying local development environment configuration.}
            \resumeItem{Developed real-time analytics for speech rate, filler-word detection, and multi-metric scoring to deliver actionable user feedback.}
            
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
           {\textbf{E. coli Fermentation Analytics} $|$ \emph{Power BI, Python, Dash, Docker, AWS(ECR, EC2, RDS, S3) }}{Aug. 2025 - June 2025}
          \resumeItemListStart
           \resumeItem{Visualized 300L E.coli batch fermentation KPIs for 21 batches at the NCSU Biomanufacturing Training and Education Center.}
           \resumeItem{Made a  \textbf{Plotly} Dash app to show Power BI snapshots alongside Prophet forecast summaries, containerized  via Docker tools. }
         
        
        \resumeItem{ Crafted \textbf{ETL} pipelines to load CSVs into PostgreSQL, update KPI tables, and write five-period forecasts.}
        \resumeItem{Deployed on \textbf{AWS} using ECR for private Docker registry, EC2 t2.micro, and Amazon RDS PostgreSQL for scalable, backed-up storage. }
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Wolf Cafe System} $|$ \emph{Java, React, SpringBoot, Hibernate, MySQL, JDBC, JWT}}{Aug. 2024 - Oct. 2024}
          \resumeItemListStart
            \resumeItem{Helped in making a \textbf{React} front end for recipe management with interactive forms and drop down menus, integrating API calls via Axios.}
            \resumeItem{Used \textbf{JWT}-based role authentication to have secure access controls for Admin, Staff, and Customer roles, supporting data privacy.}
    \resumeItem{Established CI/CD pipelines using \textbf{Github} and \textbf{Jenkins}, streamlining Maven build processes, unit test runs, and daily reporting.}
          \resumeItemListEnd
          \vspace{-13pt}
      
          \resumeProjectHeading
          {\textbf{Student Careers Dashboard} $|$ \emph{Python, Flask, SQL, SSH, SQL Alchemy, Neon}}{Jan. 2024}
          \resumeItemListStart
            \resumeItem{Developed a web application for NCSU student job positions, creating  forms with AJAX validation and \textbf{reCAPTCHA}/ v2 honeypots.}
            \resumeItem{Incorporated  \textbf{SSH} tunneling and environmental variables for secure SSL connection between app and Neon-hosted database.}
            \resumeItem{Implemented secure user authentication with Werkzeug hashing for admin/user logins and role-based dashboard analytics.}
           
          \resumeItemListEnd 

          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Speech Recognition AI} $|$ \emph{Python, Google Speech-to-Text API, Wolfram Alpha API, pyttsx3 }}{Aug. 2023}
          \resumeItemListStart
            \resumeItem{Designed an simple AI leveraging Google's Speech-to-Text API and \textbf{pyttsx3} library for accurate microphone-based voice recognition.}
            \resumeItem{Implemented command parsing algorithms for interpreting voice commands, conducting web searches, and taking notes.}
            \resumeItem{Utilized the Wolfram Alpha API  to send queries to tutoring application and process \textbf{XML/JSON} response pods/subpods efficiently.}
            
          \resumeItemListEnd 
          
          
    \resumeSubHeadingListEnd 